Scaling of leaf and above-ground woody biomass

### 2014-03-21 analysis/stem_leaf_scaling.Rnw
Added comparison between tropical and temperate evergreen angiosperms

<<plotting, echo=FALSE>>=
# natural scale
plot(1, xlim=c(0,50), ylim=c(0,1), type='n',
     xlab="Plant height (m)", ylab="Leaf mass / aboveground mass (-)")
for(i in 1:length(l))points(l[[i]]$h, l[[i]]$wfrel, type='l')

# log-log scale
plot(1, xlim=c(-3,2), ylim=c(-3,0), type='n',
     xlab="Plant height (m)", ylab="Leaf mass / aboveground mass (-)",
     axes=FALSE)
addlogaxes(10^-3, 10^2, 10^-3, 10^0, tck1=-0.03, tck2=-0.015)
for(i in 1:length(l))points(log10(l[[i]]$h), log10(l[[i]]$wfrel), type='l')

# log-natural scale
plot(1, xlim=c(-3,2), ylim=c(0,1), type='n',
     xlab="Plant height (m)", ylab="Leaf mass / aboveground mass (-)",
     axes=FALSE)
addlogaxes(10^-3, 10^2, 10^-3, 10^0, tck1=-0.03, tck2=-0.015,addY=F)
axis(2)
for(i in 1:length(l))points(log10(l[[i]]$h), l[[i]]$wfrel, type='l')

# Coloured by pft

@@

>>>>

\section{By plant functional type}

<<plotting, echo=FALSE>>=
# # natural scale
# plot(1, xlim=c(0,50), ylim=c(0,1), type='n',
#      xlab="Plant height (m)", ylab="Leaf mass / aboveground mass (-)")
# for(i in 1:length(l))points(l[[i]]$h, l[[i]]$wfrel, type='l')
# 
# # log-log scale
# plot(1, xlim=c(-3,2), ylim=c(-3,0), type='n',
#      xlab="Plant height (m)", ylab="Leaf mass / aboveground mass (-)",
#      axes=FALSE)
# addlogaxes(10^-3, 10^2, 10^-3, 10^0, tck1=-0.03, tck2=-0.015)
# for(i in 1:length(l))points(log10(l[[i]]$h), log10(l[[i]]$wfrel), type='l')
# 
# # log-natural scale
# plot(1, xlim=c(-3,2), ylim=c(0,1), type='n',
#      xlab="Plant height (m)", ylab="Leaf mass / aboveground mass (-)",
#      axes=FALSE)
# addlogaxes(10^-3, 10^2, 10^-3, 10^0, tck1=-0.03, tck2=-0.015,addY=F)
# axis(2)
# for(i in 1:length(l))points(log10(l[[i]]$h), l[[i]]$wfrel, type='l')

@@

\section{Tropical vs. temperate evergreens}

<<echo=FALSE>>=
ii <- which(P$pft == "EA" & P$vegetation %in% c("TempF","TempRF","TropRF","TropSF"))
l <- l[ii]
P <- P[ii,]

P$TempTrop <- as.factor(ifelse(P$vegetation %in% c("TempF","TempRF"), "Temp", "Trop"))
palette(c("blue","red"))

<<plotEA, echo=FALSE>>=

# log-log scale
plot(1, xlim=c(-3,2), ylim=c(0,1), type='n',
     xlab="Plant height (m)", ylab="Leaf mass / aboveground mass (-)",
     axes=FALSE)
addlogaxes(10^-3, 10^2, 10^-3, 10^0, tck1=-0.03, tck2=-0.015,addY=F)
axis(2)
for(i in 1:length(l)){
  points(log10(l[[i]]$h), l[[i]]$wfrel, type='l',
         col=P$TempTrop[i])
}
legend("bottomleft", c("Temperate evergreen angiosperm",
                       "Tropical evergreen angiosperm"), fill=palette())

plot(1, xlim=c(-3,2), ylim=c(-7,5), type='n',
     xlab="Plant height (m)", ylab="Leaf mass (kg)",
     axes=FALSE)
magaxis(side=1:2, unlog='xy',box=TRUE)
for(i in 1:length(l))points(log10(l[[i]]$h), log10(l[[i]]$mlf), type='l',
                            col=P$TempTrop[i])
legend("topleft", c("Temperate evergreen angiosperm",
                       "Tropical evergreen angiosperm"), fill=palette(),inset=0.03)

plot(1, xlim=c(-3,2), ylim=c(-7,5), type='n',
     xlab="Plant height (m)", ylab="Above-ground woody mass (kg)",
     axes=FALSE)
magaxis(side=1:2, unlog='xy',box=TRUE)
for(i in 1:length(l))points(log10(l[[i]]$h), log10(l[[i]]$mst), type='l',
                            col=P$TempTrop[i])
legend("topleft", c("Temperate evergreen angiosperm",
                       "Tropical evergreen angiosperm"), fill=palette(),inset=0.03)
